---
# YAML header created by ox-ravel
author: Shreyas Ragavan
---

# Simple project to scrape product information off the Nomatic site

I think they have a fantastic range of products and this is just an
experiment of a fan of the company and product, and a hobby project. 

Reference URL: <https://www.nomatic.com/products/the-nomatic-travel-pack>

This mini project was inspired by a question posed by the awesome [Max Humber](https://www.linkedin.com/in/maxhumber/) via Linked in.


# Environment

Renv can be used to quickly install the required libraries. Use `renv::install()`


# General plan/tasks

-   beginnings of a function to pull in all the products on multiple pages
    and pull in key descriptions for individual pages. This
-   [X] individual functions have to be plugged into a map function for
    obtaining all the product URL's
-   [ ] Product URL's have to be reviewed since there are some spurious
    products like insurance
-   [ ] table formation and info extract need to be fleshed out and
    improved
-   [ ] function to be created for individual product feature extraction


# Code demo


## Load Libraries and Source functions

```{r   }
## Loading Libraries ---
library(dplyr)
library(rvest)
library(purrr)
library(fs)
library(xopen)
library(furrr)
library(stringr)

## Source functions
source("functions.R")
 
```


## Init Variables and URL

```{r   }
## Prefix URLs
all_products_prefix_url = "https://www.nomatic.com/collections/all-products?page="
individual_product_prefix_url = "https://www.nomatic.com/products/"


## Number of pages to scrape 6
## The number of pages was manually obtained by inspection
page_range <- seq(1:6)
 
```


## Obtain All product URLs

```{r   }
all_product_url_tbl <- page_range %>% map_df(
                                        ~ consolidate_all_links_on_a_page(
  all_products_prefix_url = all_products_prefix_url,
  page_no = .x,
  individual_product_prefix_url))

all_product_url_tbl 
```


## TODO Obtaining individual product features

Using a single product url for initial exploration

```{r   }
url_test <- all_product_url_tbl[2,2] %>% pull

html <- read_html(url_test)

print(url_test) 
```

Main product features :

```{r   }
main_product_features <- html %>%
  html_nodes(".product-features") %>%
  html_nodes("li") %>%
  html_text() %>%
  str_trim() %>%
  unique() 
```

```{r   }
### Carousel details ----
carousel_details <- html %>%
  html_nodes(".accordion") %>%
  html_nodes(".accordion_body") %>%
  html_text() %>%
  str_trim() %>%
  unique() %>% 
  tibble("detailed_features" = .)

### Carousel headers
carousel_feature_names <- html %>%
  html_nodes(".accordion") %>%
  html_nodes(".accordion_head") %>%
  html_text() %>%
  str_trim() %>%
  unique() %>% 
  tibble("feature_names" = .) 

all_carousel_details_tbl <-
  bind_cols(carousel_feature_names) %>%
  bind_cols(carousel_details) 
```

